compGeometeR: an R package for computational geometry

### 2021-03-05 paper/main.tex
Updated paper

  \cmidrule{1-9} 
  Digital geometry			&     &   &     &   &   &     &   &   \\
  \cmidrule{1-9} 
  Alpha complex				& $n$ &   &     &   &   &     &   &   \\
  Alpha shape				& $n$ &   &     &   &   &     &   &   \\
  Convex hull  				& $n$ &   &     &   &   &     &   &   \\
  Delaunay triangulation	& $n$ &   &     &   &   &     &   &   \\
  \bottomrule
\end{tabular}
\label{tab:r-options}
\end{table}

@@

Discrete geometry studies the shapes and interactions between sets of discrete objects such as points, lines, circles, and polygons in 2-dimensional space.  All of the discrete computioanl geomtery algorithms in compGeometeR take as an input a set of points $P$ in $n$-dimensional Eucliden space $\mathbb{R}^n$.

@@

Digital geometry is a branch of geometry that studies the geometric properties of a grid (or lattice) of points in Euclidean space, and usually involves the digitisation of discrete lines and regions \citep{rosenfeld-1989}.

@@

>>>>

  \cmidrule{1-9} 
  Digital geometry			&     &   &     &   &   &     &   &   \\
  \cmidrule{1-9} 
  Alpha complex				& $n$ &   &     &   &   &     &   &   \\
  Alpha shape				& $n$ &   &     &   &   &     &   &   \\
  Convex hull  				& $n$ &   &     &   &   &     &   &   \\
  \bottomrule
\end{tabular}
\label{tab:r-options}
\end{table}

@@

Discrete geometry studies the shapes and interactions between sets of discrete objects such as points, lines, circles, and polygons in 2-dimensional space.  All of the discrete computioanl geomtery algorithms in compGeometeR take as an input a set of points $P$ in $n$-dimensional Euclidean space $\mathbb{R}^n$.

@@

Digital geometry is a branch of geometry that studies the geometric properties of a grid (or lattice) of points in Euclidean space, and usually involves the digitisation of discrete lines and regions \citep{rosenfeld-1989}.  Digitisation occurs by representing Euclidean space $\mathbb{R}^n$ as a a rectangular orthogonal grid $\mathbb{G}^n$.  The elements of $\mathbb{G}^2$ are called pixels, and the elements of $\mathbb{G}^3$ are called voxels \citep{klette-2004}.  Each element in $\mathbb{G}^n$ has a grid coordinate for its centre, and a value that denotes if the element belongs to digitised geometric object, or when required which part of the digitised geometric object.

@@

[Note inclusion of the Voronoi diagram for discrete geometry algorithms, and making more of the discrete algorithms available in digital form.]
